Draft

### 2016-07-27 Draft/draft.tex
Update QFT in a Nutshell. Move this note outside "Draft.tex".

\section{Quantum Field Theory in a Nutshell}
\label{sec:Quantum_Field_Theory_in_a_Nutshell}
    \subsection{Part I: Motivition and Foundations}
    \label{sec:QFT_in_a_Nutshell.Part_I}
        \subsubsection{I:2 Path Integral Formulation of Quantum Physics}
        \label{sec:QFT_in_a_Nutshell_Part_I.2}
        Here the path integral formulation of quantum mechanics is introduced.
        The intuition comes from a limiting case of the traditional double 
        slit electron interference experiment. (\textbf{pp.7 to 10}) Then 
        it calculates the transition probability $\braket{q_F|e^{-iHT}|q_I}$
        by divide it into a infinite of steps:
        \begin{align}
            \braket{q_F|e^{-iHT}|q_I} = \lim_{N\to \infty}
            \braket{q_F|e^{iH\delta t}e^{iH\delta t}\cdots e^{iH\delta t}|q_I}
            (\text{with }N\delta t = T)
        \end{align}

        For illustration, it calculates this value when 
        $H=\frac{\hat{p}^2}{2m}$. The result is that:
        \begin{align*}
            \braket{q_F|e^{-iHT}|q_I} = \int Dq(t) 
                e^{i\int_0^T dt \frac{1}{2}m \dot{q}^2 }
        \end{align*}

        where:
        \begin{align}
            \int Dq(t) \equiv \lim_{N\to \infty} 
            \left( \frac{-im}{2\pi \delta t}\right)^{N/2}
            \left( \prod_{k=1}^{N-1} \int dq_k \right)
        \end{align}
        It notes that when $H=\hat{p}^2/2m + V(\hat{q})$, the final result
        would have been:
        \begin{align}
            \label{eq:QFT_in_a_Nutshell_Part_I.2.TransProbability}
            \braket{q_F|e^{-iHT}|q_I} &= \int Dq(t) 
                e^{i\int_0^T dt \frac{1}{2}m \dot{q}^2 - V(q)}
                \nonumber \\
                &= e^{i \int_0^T dt L(\dot{q}, q)}
        \end{align}
        where $L$ is the Lagrangian of the system.

        The value \(\braket{0|e^{-iHT}|0}\) is denoted $Z$. This part
        mentions that one often effect a change of coordinate
        $t \to -it$, called \textit{Wick rotation}, to obtain:
        \begin{align}
            Z = \int Dq(t) e^{-\int_0^T dt H(\dot{q},q)}
        \end{align}
        where $H$ is the Hamiltonian of the system.
        The mathematical rigorious aspect is often ignored.

        It also discuss how this formulation could explain the classical
        limit of quantum mechanics, i.e. classical mechanics, in a
        very direct manner. This is related to the saddle point
        approximation to the integral 
        \ref{eq:QFT_in_a_Nutshell_Part_I.2.TransProbability}.

        \paragraph{Unclear point}
        Why is $\int dq \ket{q}\bra{q} = 1$ while $\int \frac{p}{2\pi}
        \ket{p}\bra{p} = 1$. What does it mean by saying
        "to see that the normalization is correct" (pp. 10 and 11).

        \paragraph{Corresponding pages in draft} pp. 1 to 3.

\section{Miscellnaneous Math}
\label{sec:Miscellnaneous_Math}
\subsection{\texorpdfstring{$\int_0^\infty \frac{\sin(x)}{x}$}{}}
From \href{http://math.stackexchange.com/questions/5248/solving-the-integral-int-0-infty-frac-sinxx-dx-frac-pi2}{Math.SE}. By Aryabhata (http://math.stackexchange.com/users/1102/aryabhata).

>>>>

\section{Miscellnaneous Math}
\label{sec:Miscellnaneous_Math}
\subsection{\texorpdfstring{$\int_0^\infty \frac{\sin(x)}{x}$}{}}
From \href{http://math.stackexchange.com/questions/5248/solving-the-integral-int-0-infty-frac-sinxx-dx-frac-pi2}{Math.SE}. 
By \href{http://math.stackexchange.com/users/1102/aryabhata}{Aryabhata}.
